Transparent Changes

### 2022-05-02 scripts/review.Rmd
Update flow diagram

@@

This script closely follows the preregistration, which is uploaded on OSF.

```{r setup}
# Packages used for the data workflow

library(readxl)
library(rentrez)
library(XML)
library(purrr)
library(ggplot2)
library(MetBrewer)
```

@@

Removed because of missing DOI: `r no_doi_count`
Duplicates removed: `r dupl_count`

@@

Removed by automated title filtering: `r title_excl_count`
Remaining articles for random sampling: `r forsample_count`

@@

save(sampled_data, file = "../data/screen/sample.Rda")
```

@@

# Create blinded abstract plots
purrr::walk(
  .x = seq_len(nrow(sampled_data)),
  .f = create_abstract_plot, 
  data = sampled_data
)

@@

s_res <- purrr::map2_chr(s_res1, s_res2, comp_res)
s_res_df <- data.frame(
  id = 1:500,
  i1 = s_res1,
  i2 = s_res2,
  result = s_res,
  decision = rep.int("", 500),
  doi = sampled_data$doi
)
# write.csv(s_res_df, "../data/screen/abstract_screening.csv")
# Calculate relative agreement
1 - (sum(s_res == "XXX", na.rm = TRUE) / length(s_res))

@@

# write file for full text screening
ft_screen_df <- data.frame(
  sid = ft_screen$sid,
  fulltext_exclusion = rep.int("", nrow(ft_screen)),
  exclusion_note = rep.int("", nrow(ft_screen)),
  doi = ft_screen$doi
)
# write.csv(ft_screen_df, file = "../data/screen/fulltext_screening_i1.csv", row.names = FALSE)
```

@@

f_res <- purrr::map2_chr(f_res1, f_res2, comp_res)
f_res_df <- data.frame(
  sid = f_res_i2$sid,
  i1 = f_res1,
  i2 = f_res2,
  result = f_res,
  decision = rep.int("", length(f_res1)),
  i1_note = f_res_i1$exclusion_note,
  i2_note = f_res_i2$exclusion_note,
  doi = f_res_i1$doi
)
# write.csv(f_res_df, "../data/screen/fulltext_screening.csv", row.names = FALSE)
# Calculate relative agreement
1 - (sum(f_res == "XXX", na.rm = TRUE) / length(f_res))

@@

# read final decision
ft_res <- read.csv("../data/screen/fulltext_screening.csv")
ft_res$decision <- factor(
  ft_res$decision, 
  levels = c("t", "l", "r", "h", "m", "c", "e", "d", "o"),
  labels = c("no fulltext", "no english full-text", "no original research", 
             "no humans", "VO2 not measured", "VO2 not continously measured", 
             "no exhaustion", "long protocol", "other")
)
# count exclusions
ft_excl_count <- sum(!is.na(ft_res$decision))

@@

@@

save(reporting, file = "../data/reporting.Rda")

@@

```{r analysis}
# Show data processing strategies overall
table(ext$ptype, useNA = "ifany")

@@

# Plot for total calculation interval lengths
ext[ext$ptype == "time" & !is.na(ext$ptype), ] |>
  ggplot(aes(y = param_duration)) +
    geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", hjust = 1.2, colour = "white") +
    scale_y_reverse(
      breaks = c(5, 10, 15, 20, 30, 45, 60),
      minor_breaks = NULL,
      name = "Duration (s)"
    ) +
    scale_x_continuous(
      minor_breaks = NULL,
      name = "Count",
      breaks = c(0, 10, 20, 30, 40),
      labels = NULL,
      expand = c(0, 0),
      position = "top"
    ) +
    theme_minimal(13) +
   theme(
     panel.grid.major.y = element_blank(),
     axis.ticks.y = element_line(colour = "grey", size = 0.5)
    )

ggsave("../plots/duration_count.png", width = 5, height = 3, dpi = 600, bg = "white")
```

```{r}
library(treemapify)
library(dplyr)
library(colorspace)

@@

ggplot(ext_count, aes(area = n, fill = proc_combination, label = label, subgroup = subgroup)) +
  geom_treemap(show.legend = FALSE, start = "topleft") +
  geom_treemap_text(
    color = "black",
    reflow = TRUE, 
    place = "centre", 
    start = "topleft",
    padding.y = grid::unit(1.5, "mm")) +
  scale_fill_manual(
    values = colorspace::lighten(c("#663171", "#ea7428", "#653151", "#0c7156", "#0c7182"), amount = 0.2)
  )

ggsave("../plots/strategies.png", width = 5, height = 3, dpi = 600, bg = "white")
```

>>>>

---
title: ''
output: github_document
bibliography: ../references.bib
---

@@

This script closely follows the preregistration, which is uploaded on the [OSF](https://osf.io/3am4s).

```{r setup, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(out.width = "70%", fig.align = "center")

# Packages used for the data workflow
library(readxl)
library(rentrez)
library(XML)
library(purrr)
library(dplyr)
library(ggplot2)
library(MetBrewer)
library(treemapify)
library(colorspace)
```

@@

Removed because of missing DOI: `r no_doi_count`

Duplicates removed: `r dupl_count`

@@

Removed by automated title filtering: `r title_excl_count`

Remaining articles for random sampling: `r forsample_count`

@@

# save(sampled_data, file = "../data/screen/sample.Rda")
```

@@

# Create blinded abstract plots
# purrr::walk(
#   .x = seq_len(nrow(sampled_data)),
#   .f = create_abstract_plot, 
#   data = sampled_data
# )

@@

s_res <- purrr::map2_chr(s_res1, s_res2, comp_res)
s_res_df <- data.frame(
  id = 1:500,
  i1 = s_res1,
  i2 = s_res2,
  result = s_res,
  decision = rep.int("", 500),
  doi = sampled_data$doi
)
# write.csv(s_res_df, "../data/screen/abstract_screening.csv")

# Calculate relative agreement
1 - (sum(s_res == "XXX", na.rm = TRUE) / length(s_res))

@@

# write file for full text screening
ft_screen_df <- data.frame(
  sid = ft_screen$sid,
  fulltext_exclusion = rep.int("", nrow(ft_screen)),
  exclusion_note = rep.int("", nrow(ft_screen)),
  doi = ft_screen$doi
)

# write.csv(ft_screen_df, file = "../data/screen/fulltext_screening_i1.csv", row.names = FALSE)
```

@@

f_res <- purrr::map2_chr(f_res1, f_res2, comp_res)
f_res_df <- data.frame(
  sid = f_res_i2$sid,
  i1 = f_res1,
  i2 = f_res2,
  result = f_res,
  decision = rep.int("", length(f_res1)),
  i1_note = f_res_i1$exclusion_note,
  i2_note = f_res_i2$exclusion_note,
  doi = f_res_i1$doi
)

# write.csv(f_res_df, "../data/screen/fulltext_screening.csv", row.names = FALSE)

# Calculate relative agreement
1 - (sum(f_res == "XXX", na.rm = TRUE) / length(f_res))

@@

# read final decision
ft_res <- read.csv("../data/screen/fulltext_screening.csv")
ft_res$decision <- factor(
  ft_res$decision, 
  levels = c("t", "l", "r", "h", "m", "c", "e", "d", "o"),
  labels = c("no fulltext", "no english full-text", "no original research", 
             "no humans", "VO2 not measured", "VO2 not continously measured", 
             "no exhaustion", "long protocol", "other")
)

# count exclusions
ft_excl_count <- sum(!is.na(ft_res$decision))

@@

table(ft_res$decision, useNA = "ifany")

@@

# save(reporting, file = "../data/reporting.Rda")

@@

#### Plot: Calculation intervals

```{r interval, warning = FALSE}
# Show data processing strategies overall
table(ext$ptype, useNA = "ifany")

@@

# Plot for total calculation interval lengths
p_int <- ext[ext$ptype == "time" & !is.na(ext$ptype), ] |>
  ggplot(aes(y = param_duration)) +
    geom_bar() +
  geom_text(aes(label = ..count..), stat = "count", hjust = 1.2, colour = "white") +
    scale_y_reverse(
      breaks = c(5, 10, 15, 20, 30, 45, 60),
      minor_breaks = NULL,
      name = "Duration (s)"
    ) +
    scale_x_continuous(
      minor_breaks = NULL,
      name = "Count",
      breaks = c(0, 10, 20, 30, 40),
      labels = NULL,
      expand = c(0, 0),
      position = "top"
    ) +
    theme_minimal(13) +
   theme(
     panel.grid.major.y = element_blank(),
     axis.ticks.y = element_line(colour = "grey", size = 0.5)
    )

# ggsave(p_int, "../plots/duration_count.png", width = 5, height = 3, dpi = 600, bg = "white")

knitr::include_graphics("../plots/duration_count.png")
```

#### Plot: Processing strategies

```{r strategies}

@@

p_strat <- ggplot(ext_count, aes(area = n, fill = proc_combination, label = label, subgroup = subgroup)) +
  geom_treemap(show.legend = FALSE, start = "topleft") +
  geom_treemap_text(
    color = "black",
    reflow = TRUE, 
    place = "centre", 
    start = "topleft",
    padding.y = grid::unit(1.5, "mm")) +
  scale_fill_manual(
    values = colorspace::lighten(c("#663171", "#ea7428", "#653151", "#0c7156", "#0c7182"), amount = 0.2)
  )

# ggsave(p_strat, "../plots/strategies.png", width = 5, height = 3, dpi = 600, bg = "white")

knitr::include_graphics("../plots/strategies.png")
```
